### 2017-05-31 paper.tex
Update paper.tex

Technical lessons development is hindered by several core problems. 
Lessons can quickly become outdated, buggy, or fail to be updated. 
Collaborative code development offers a pathway forward, allowing us to 
create lessons which are both open and accessible, as well as 
being continually maintained, refined, and improved by a large
community of contributors. This paper provides ten simple rules that can help
others create sustainable lessons.

>>>>

Technical lessons development is hindered by several core problems. 
Lessons can quickly become outdated, buggy, or fail to be updated. 
Collaborative code development offers a pathway forward, allowing us to 
create lessons which are both open and accessible, as well as 
being continually maintained, refined, and improved by a large
community of contributors. This paper provides ten simple rules that can help
others create sustainable lessons. 
Our ten rules focus on both the people and the mechanisms involved with 
lesson development. First, we describe the importance of clarifying audiences, 
building communities around lessons, teaching people how to develop lessons, 
and empowering lesson contributors. Then we describe the utility of 
building modular lessons, reusing lesson materials, pointing to external resources, 
and publishing materials periodically. Finally, we encourage that all outcomes 
are evaluated and assessed to ensure continues success of the program or 
find new avenues for improvement.
